

\fancyhf{} % clear all header and footer fields
\fancyhead[RO,R]{\thepage} %RO=right odd, RE=right even
\renewcommand{\headrulewidth}{0pt}

\begin{center}
    \Large
    \textbf{Sokoban: History and AI}

    \vspace{0.4cm}
    \large
    Thesis Subtitle

    \vspace{0.4cm}
    \textbf{Author Name}

    \vspace{0.9cm}
    \textbf{Abstract}
\end{center}

This thesis examines the role of input compression methods in improving agent performance
within PuzzleJAX, a GPU-accelerated puzzle-solving benchmark for AI reasoning. Prior work in
game-playing agents has shown that compressed input representations using the Discrete
Cosine Transform (DCT) can outperform conventional reinforcement learning models by
achieving a higher score with a lower weight count. This thesis extends these ideas to Boxoban,
a Sokoban level dataset by Google. Previous studies have yet to explore input type and
compression method on sokoban games, motivating the use of novel input compression
techniques in the study.


This project evaluates several input compression strategies, including frequency domain
transforms and autoencoder embeddings. These compression techniques are used for training
both the policy network and the value network. The police network is trained on solution
trajectory of Boxoban levels found through Breath First Search and the value network is trained
with reinforcement learning, bootstrapping the policy network through AlphaGo-styled tree
search. The findings highlight appropriate compression strategies that improve agent
performance in planning-intensive tasks.