\section{Invention of Sokoban}
Sokoban is a widely successful puzzle game where the goal is to push boxes around in a warehouse to position it in correct places. However, the position of each boxes determine the mobility of other boxes and the player. In some cases, the player may accidentally push the box into a corner rendering it completely immobile. \cite{junghanns1999pushing} Due to these restrictions, players are required to plan ahead of moving to successfully solve each level.

The game was invented in 1981 by Hiroyuki Imabayashi as hobby and it was commercially released in 1982. Since its release, the series has sold over 4.1 million copies worldwide, with over 40 official games and countless clones, enabled by the simplistic gameplay design. 

\section{Gameplay}
Sokoban is a top-down puzzle game where the player controls a 2d character in a warehouse with several boxes that the player can push. Some tiles are marked as storage locations where the boxes in the level need to be placed. In order to complete the level, all boxes needs to be placed on a designated tiles. \cite{murase1996automatic} The levels are generally surrounded with tight walls and the boxes are as large as the player. This often means that the boxes can block paths and the player often needs to relocate the box in order to reach to certain areas in the level. This is made more difficult by the fact that the player can only push the boxes and is unable to pull. If a box is pushed onto a wall, the player can only move the box tangent to the wall as they can not push away from the wall. \cite{sokoban_official_whatis} If the box is pushed into a corner, the box can not be moved for the same reason. \cite{micomgames1983sokoban} If this was not part of the solution, the player would reach a deadend and the only way to progress is to reset the current level or undo the previous move. 

\section{History}
The first iteration of the game operated on NEC-8001 as a hobby by Hiroyuki Imabayashi. \cite{login1983thinkingrabbit} The was primarily inspired by \textit{Aldebaran \#1 } created by Hudson Soft where the player pushed objects to block radiation. \cite{monthlymycom1980aldebaran} \cite{aguilera2020imabayashi} However, Hiroyuki envisioned a more difficult game where objects could be stuck at specific places; a game mechanic less explored in \textit{Aldebaran \#1} due to its spacious levels. \cite{sokoban_official_greetings} The hobby project became a commercial project when a salesman came across it in a store owned by Hiroyuki's parents-in-law. Since its original launch in NEC PC-8801, \cite{popcom1984visiting} the game was revisioned many times across various platforms, to handheld gaming consoles like Game Boy \cite{atelier_double_history_1989} to consumer computers like Apple II \cite{ellison1988whyjapan} and Windows \cite{sokoban_smart_official} and most recently, Nintendo Switch and PlayStation 4. \cite{sokoban_official_lineup}

\section{Reception}
The Sokoban instantly became the favorite of puzzle enthusiasts \cite{tanaka1986thesokoban} with over 25,000 copies sold by July 1984 from the initial release in Japan. \cite{popcom1984strategy} It was quickly followed by multiple successful releases in Japan which prompted a global release. The U.S. release \textit{Soko-Ban}, sold over 50,000 opcies by mid-September 1988. \cite{ellison1988whyjapan} By 2018, the series had sold over 4.1 million copies worldwide. \cite{atpress2018chukyo}

Sokoban was praised for its addictive simplistic gameplay combined with difficult puzzles that require high level of planning on the level  or Shogi. \cite{micomgames1983sokoban} The popularity and the difficulty combined soon lead to a study on understanding the nature of Sokoban as a problem from the computational complexity theory point of view.

The difficulty was soon studied with computational complexity theory by Fryers et al and the result was published in 1995 on Eureka. \cite{fryers1995sokoban} Sokoban was found to be NP-hard which indicates that any NP problem can be encoded into a Sokoban in polynomial time. In other words, theoratically, finding a generic solution to all sokoban puzzle indicates that the logic required to solve puzzle can be applied to any other easier NP problems, proving that any NP problem is a P problem which are trivial to solve. While it is widely thought to be that NP is not P, searching for a solution to a NP-hard problem has the academic significance that its solution may be applied to some other specific problems. Similarily to how AlexNet triggered the Deep Learning revolution in the 2010s while trying to solve an image classification problem, \cite{krizhevsky2012imagenet} academia is always searching for an interesting problem to solve in an interesting perspective that would push the boundaries of science in unexpected ways. \cite{lecun2015deep} For this reason, Sokoban is an academically interesting problem. The next chapter discusses the variety of methodology the researchers have been applying to solve sokoban.