\section{PSPACE-complete}
We have shown that Sokoban is a difficult and valid academic problem by showing that it is an $NP-hard$ problem, following the proof from Fryers et al. \cite{fryers1995sokoban} \cite{cook2023complexity} As well as being an NP-hard game, Sokoban was also found to be PSPACE-complete. \cite{culberson1997sokoban} A PSPace problem is a decision problem that can be solved by a Turing machine using a polynomial amount of memory space. If every problem P in PSPACE can be reduced to a problem, the problem is PSPACE-hard. A problem is PSPACE-complete if and only if it is a PSPACE and a PSPACE-hard problem.

Culberson demonstrated that Sokoban is a PSPACE-Complete problem by recreating a finite tape Turing Machine in Sokoban. \cite{culberson1997sokoban} To create the emulator, the researcher relied on two basic properties of the game. The first is the notion of unrecoverable configuration. This is when it is not possible to move a box to its goal position either because the box was placed in a deadend location or if the goal position is impossible to reach due to its placement. The second is the fact that the player movement is also bound by the geometry of the puzzle. Then,/ several gadgets are introduced, similarly to the NP-hard proof. Eahc gadget is a section of Sokoban puzzle. These gadgets are combined into Cellular Units representing one cell of the finite Turing Machine's tape. Culberson proves that the puzzle created from these Cellular Units has the solution if and only if the emulated Turing Machine halts in an "accept" state. 